Empty Homes V1

### 2017-06-06 EmptyHomesV1.Rmd
Bootstrapped results
Bootrapped results are working properly

round(table(ChelPrice$class)/nrow(ChelPrice)*100)

set.seed(16544)
Chelseastrapped <- ClassStrapper(ChelPrice, sum(Chelseainfo$LowUse))

Chelseastrapped %>% group_by(class)%>%
  summarise(Counts = mean(Counts)) %>%
  mutate(ratio = Counts/sum(Counts))

Chelseastrapped %>% ggplot(., aes(x= class, y = Counts, fill = class)) + geom_boxplot()

ChelseainfoWard <- Chelseainfo %>%
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first))

set.seed(16540)
ChelseaLSOAstrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  )

ChelseaLSOAstrap <- ChelseaLSOAstrap1 %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

#bootrapps Chelsea housing stock.
set.seed(16540)
ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

test1 <- Chelseastrapped %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
  mutate(ratio = Totals/Counts)

test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
  rename(LowUse = Totals.y,
         Homes = Totals.x) %>%
  group_by(ID)%>%
  mutate(ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes),
         LowUsePerc = LowUse/sum(LowUse),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse),
         RatioExvsAct = LowUse/ExpectedHomes)

@@

test1 %>% ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Boxplot of bootstrapped Ratios")

test1 %>% group_by(class) %>%
  summarise(meanC = mean(Counts), 
            meanT = mean(Totals), 
            meanR = mean(ratio))

ChelseaWardHomesStrap1 %>% group_by(class) %>%
  summarise(meanC = mean(Totals))

>>>>

#bootrapps Chelsea housing stock.
set.seed(16546)
ChelseaWardLowUseStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse), reps = 10000) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

#bootrapps Chelsea housing stock.
set.seed(16540)
ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes), reps = 10000) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaWardLowUseStrap1, by = c("class", "ID")) %>%
  rename(LowUse = Totals.y,
         Homes = Totals.x) %>%
  group_by(ID)%>%
  mutate(ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes),
         LowUsePerc = LowUse/sum(LowUse),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse),
         RatioExvsAct = LowUse/ExpectedHomes)

@@

test1 %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
SaveFig("DistributionPlot.png")

test1 %>% group_by(class) %>%
  summarise_all(funs(mean))
